\documentclass[12pt,twoside,notitlepage]{report}

\usepackage{a4}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[font={small,it}]{caption}
\usepackage{pdfpages}
\raggedbottom                           % try to avoid widows and orphans
\sloppy
\clubpenalty1000%
\widowpenalty1000%

\addtolength{\oddsidemargin}{6mm}       % adjust margins
\addtolength{\evensidemargin}{-8mm}

\renewcommand{\baselinestretch}{1.1}    % adjust line spacing to make

\begin{document}

\bibliographystyle{plain}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title


\pagestyle{empty}

\hfill{\LARGE \bf Karina Palyutina}

\vspace*{60mm}
\begin{center}
\Huge
{\bf Machine learning inference of search engine heuristics} \\
\vspace*{5mm}
Part II Project \\
\vspace*{5mm}
St Catharine's College \\
\vspace*{5mm}
\today  % today's date
\end{center}

\cleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Proforma, table of contents and list of figures

\setcounter{page}{1}
\pagenumbering{roman}
\pagestyle{plain}

\chapter*{Proforma}

{\large
\begin{tabular}{ll}
Name:               & \bf Karina Palyutina                       \\
College:            & \bf St Catharine's College                     \\
Project Title:      & \bf Machine learning inference of search engine heuristics \\
Examination:        & \bf Part II Project        \\
Word Count:         & \bf \footnotemark[1]     \\
Project Originator: & Dr Jon Crowcroft                    \\
Supervisor:         & Dr Jon Crowcroft                  \\ 
\end{tabular}
}
\footnotetext[1]{This word count was computed
by {\tt detex diss.tex | tr -cd '0-9A-Za-z $\tt\backslash$n' | wc -w}
}
\stepcounter{footnote}

\newpage


\section*{Original Aims of the Project}


\section*{Work Completed}


\section*{Special Difficulties}

\section*{Declaration of Originality}

I, Karina Palyutina of St Catharine's College, being a candidate for Part II of the Computer
Science Tripos , hereby declare
that this dissertation and the work described in it are my own work,
unaided except as may be specified below, and that the dissertation
does not contain material that has already been used to any substantial
extent for a comparable purpose.

\bigskip
\leftline{Signed }

\medskip
\leftline{Date }

\cleardoublepage

\tableofcontents


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% now for the chapters

\cleardoublepage        % just to make sure before the page numbering
                        % is changed

\setcounter{page}{1}
\pagenumbering{arabic}
\pagestyle{headings}

\chapter*{Introduction}
This project is inspired by increasing importance of search engine rankings.
Today major search engines given a query return web pages in an order
determined by secret algorithms. Such algorithms are believed 
to incorporate multiple unknown factors.
For instance, Google claims to have over 200 unique factors that influence a
position of a webpage in the search results relative to a query
\footnote{http://www.google.com/competition/howgooglesearchworks.html}. Only
a handful of these factors are disclosed to the webmasters  in the form of very
general guidelines. Moreover, the Google algorithm in particular is updated
frequently. However, most of the knowledge around the area amounts to
speculation. Despite the fact that it is possible to pass a vast number of
queries through the black box of any existing search engine,the immensity of
the search space, and instability of such algorithms make them impossible to
reverse engineer.

Machine learning is a natural approach to inferring the true algorithm from a
subset of all possible observations. However, applying machine learning
techniques to real search engines would be hardly effective, as the dynamic
nature of the algorithms and the web as well as lack of meaningful feedback
would prevent incremental improvement: when there are as many as 200 features
in question, false assumptions made by a learner may have an unpredictable
effect on its performace.

More generally, there are certain ambiguities associated with machine learning,
which are 'problem-specific'. For example, it proves difficult to decide how
much training data is necessary, as well as and selecting it to avoid
over/under-fitting\cite{DOMINGOS}. Similarly, it is not straightforward which
machine learning technique is best for a particular problem.

This project is concerned with application of machine learning techniques to
search engines. The aim of the project, in particular,  is to explore how
machine learning techniques can be used effectively to infer algorithms from
search engines. To address the limitations imposed by existing search engines,
part of the task is to develop a toy search engine that allows me to comtrol
the nature and complexity of used heuristics. Such transparency addresses the
problems stated above and, more importantly,  allows for useful evaluation of
machine learning techniques by providing meaningful feedback.

Even though this study does not attempt to reverse engineer any existing
heuristics, the results can be applied to such an ambitious task.
Moreover, such a framework is potentially more general and can be used for a
range of problems. 


\cleardoublepage
\chapter*{Preparation}


\cleardoublepage
\chapter*{Implementation}
This section describes parts of the system that I have implemented.

\section{Search Engine}
Overview

\subsection{PageRank}
\subsection{Indexer}
\subsection{Optimization}

\section{Parser}

\section{Machine Learning}
Overview
\subsection{Naive Bayes}

\subsection{Support Vector Machine}

\cleardoublepage
\chapter*{Evaluation}


\cleardoublepage
\chapter*{Conclusion}

\cleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% the bibliography

\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{refs}
\cleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% the appendices
\appendix

\chapter{Project Proposal}

%\input{propbody}

\end{document}
